%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  %---------------------------------------------------------
    \cventry
      {Junior Quantitative Developer} % Job title
      {Akuna Capital} % Organization
      {Boston, MA} % Location
      {Jul. 2018 - Present} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Completely overhauled live platform for reporting trade quality, including data generation, data storage, and data access.}
          \item {Implemented generic Map-Reduce framework in Python for parsing terabytes of daily platform data to replace legacy access systems.}
          \item {Created several datasets using previous framework for 100x speedup of data access, enabling previously inaccessible research.}
          \item {Contributed to firm-wide data design and access patterns for research, communicating with technical and non-technical liasons.}
          \item {Acted as go-to resource for employees in research-only Boston office about the structure and nuances of options trading.}
        \end{cvitems}
      }
  %---------------------------------------------------------
    \cventry
      {Derivatives Trading Intern: S\&P} % Job title
      {Optiver US} % Organization
      {Chicago, IL} % Location
      {Jun. 2017 - Aug. 2017} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Built a framework to analyze broker trades and retreats to maximize profit-and-loss on the S\&P Index products desk.}
          \item {Completed a ten-week derivatives trading education program, covering topics from basic Black-Scholes pricing models to trading strategies.}
          \item {Completed five weeks of simulated trading in index options products (ES) - trading weekly and monthly expiries.}
          \item {Shadowed traders for one hour each day on a variety of different products on both liquidity-providing and liquidity-taking desks.}
        \end{cvitems}
      }
  %---------------------------------------------------------
    \cventry
      {Founder \& IOS Engineer} % Job title
      {Andersen Mobile Labs} % Organization
      {Williamstown, MA} % Location
      {Feb. 2016 - Jun. 2018} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {\textit{Eph Meals}: an iOS app to serve Williams College's daily dining services menus, now with over 2000 downloads (Swift).}
          \item {\textit{OnForte}: a dual iOS and web music player application, complete with web-based backend datastore (Swift, Objective-C, Javascript).}
        \end{cvitems}
      }
%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Vistaprint US (Cimpress)} % Organization
    {Waltham, MA} % Location
    {May '15 - Sep. '15, Jun. '16 - Nov. '16} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a full-stack application to digitally inspect incoming customer documents. Impact: over 3m inspections, \$3.5m in costs saved.}
        \item {Developed an internal API service portal and deployed an open- source API gateway. Full-stack JavaScript. }
        \item {Worked on algorithmic implementations for rendering embroidery designs. Back-end TypeScript (JavaScript).}
      \end{cvitems}
    }
%---------------------------------------------------------
\cventry
{Teacher's Assistant}
{Williams College}
{Williamstown, MA}
{2015-2017}
{
\begin{cvitems}
\item \textit{Math: Probability: 341}: Held office hours and graded homeworks for students in post-linear algebra curricular core class.
\item \textit{CS: Intro: 135}: Held lab and office hours for students, graded homeworks and labs. Python.
\item \textit{CS: Intro: 134}: Held lab and office hours for students, graded homeworks and labs. Java.
\end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
